Evaluation

### 2018-02-16 evaluation.Rmd

This graph shows the forecast error of some recent forecasts for the most recent sampling dates. This is shown for all model types in the columns and several common rodent species (and total rodents) in the rows. These evaluations are for the Control plots where no manipulation is done. 
```{r recent_eval, echo=FALSE, message=TRUE, warning=FALSE,, fig.width=15, fig.height=15}
###############################################
#Get all the recent forecasts
forecast_data = compile_forecasts(use_hindcasts = FALSE) %>%
  filter(model %in% models_of_interest)

@@

```{r hindcast_eval, echo=FALSE, message=TRUE, warning=FALSE,, fig.width=9, fig.height=15}

>>>>

This graph shows the forecast error of some recent forecasts for the most recent sampling dates. This is shown for all model types in the columns and several common rodent species (and total rodents) in the rows. These evaluations are for the Control plots where no manipulation is done. 
```{r recent_eval, echo=FALSE, message=FALSE, warning=FALSE,, fig.width=15, fig.height=15}
###############################################
#Get all the recent forecasts
forecast_data = compile_forecasts(use_hindcasts = FALSE) %>%
  filter(model %in% models_of_interest)

@@

```{r hindcast_eval, echo=FALSE, message=FALSE, warning=FALSE,, fig.width=9, fig.height=15}
